\documentclass{article} % For LaTeX2e
\usepackage{nips15submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{lineno}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[all]{hypcap} 
%\linenumbers% Uncomment for line numbers



\title{Big Data, Big Problems-Parallel Kmeans}


\author{
Reuben K. McCreanor \\
Department of Statistics\\
Duke University\\
Durham, NC 27708 \\
\texttt{reuben.mccreanor@duke.edu} \\
\And
Wei (Emily) Shao\\
Department of Statistics\\
Duke University\\
Durham, NC 27708 \\
\texttt{wei.shao@duke.edu} \\
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Sharelatex Example},
    bookmarks=true,
    pdfpagemode=FullScreen,
}


\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\nipsfinalcopy 

\begin{document}

\maketitle

\begin{abstract}
ADD ABSTRACT HERE
\end{abstract}

\section{Introduction}
\label{headings}


\section{Discussion of Methods}
\label{headings}


\section{Results}
\label{headings}

\subsection{Predicting Airline Delay}


\clearpage
\newpage


\subsubsection*{References}


\hypertarget{Ref1}{[1] American Statistical Association. \textit{Data Expo 2009}. Statistical Computing and Statistical Graphics. Accessed October 20, 2015. \url{http://stat-computing.org/dataexpo/2009/the-data.html}.}

\hypertarget{Ref2}{[2]} National Oceanic and Atmospheric Administration. \textit{Air Traffic}. Science on a Sphere. Accessed October 30, 2015. \url{http://sos.noaa.gov/Datasets/dataset.php?id=44}.

\hypertarget{Ref3}{[3]} Ball, Michael et. al. \textit{Total Delay Impact Study: A Comprehensive Assessment of the Costs and Impacts of Flight Delay in the United States}. The National Center of Excellence for Aviation Operations Research (NEXTOR), October 2010.

\hypertarget{Ref4}{[4]} Socrata. \textit{Airport Codes mapped to Latitude and Longitude in the United States}. Open Data. Accessed November 10, 2015. \url{https://opendata.socrata.com/dataset/Airport-Codes-mapped-to-Latitude-Longitude-in-the-/rxrh-4cxm}.

\hypertarget{Ref5}{[5]}United States Department of Transportation. \textit{On-Time Performance}. Bureau of Transportation Statistics. Accessed November 15, 2015. \url{http://www.transtats.bts.gov/Fields.asp?Table_ID=236}.

\hypertarget{Ref6}{[6]}American Statistical Association. \textit{Data expo 2009 Supplementary Data}. Statistical Computing and Statistical Graphics. Accessed November 14, 2015. \url{http://stat-computing.org/dataexpo/2009/supplemental-data.html}.

\hypertarget{Ref7}{[7]} Link for Shiny App: \url{https://reuben.shinyapps.io/Airline_Delay_Comparison}.

[8] United States Department of Transportation. \textit{Understanding the Reporting of Causes of Flight Delays and Cancellations}. Bureau of Transportation Statistics. Accessed November 20, 2015. \url{http://www.rita.dot.gov/bts/help/aviation/html/understanding.html}.

\hypertarget{Ref9}{[9]} Federal Aviation Administration. \textit{Types of Delay}. Accessed November 18, 2015 \url{http://aspmhelp.faa.gov/index.php/Types_of_Delay}.

\clearpage
\newpage

\section{Appendix}
\label{headings}


\subsection{OLS, LASSO and Ridge Regression Methods}
\label{appendix_regression}



\end{document}


